### 2018-04-20 Manuscript/chapter4.tex
Add litre plots

Mortality rates of honeybees 72 hour post-inoculation significantly differed among the treatment groups (mixed model ANOVA across all treatment groups, df=3, 55; F=10.07; p<2.18e-05). The effect of virus treatment (mixed model ANOVA, df=1, 55; F=24.343; p<7.84e-06) and diet treatment (mixed model ANOVA, df=1, 55; F=5.796; p<0.0194) were significant, but the interaction between the two factors (mixed model ANOVA, df=1, 55; F=0.062, p=0.8039) was not significant. The virus treatment was significant: For a given diet, honeybees exposed to the virus showed significantly higher mortality rate than honeybees not exposed to the virus (Tukey HSD, p<0.05). Without virus exposure, there was only a numerical reduction in mortality rate for bees fed Castanea pollen compared to Rockrose pollen (Tukey HSD, p>0.05). Similarly, with virus exposure, there was only a numerical reduction in mortality rate for beeds fed Castanea pollen compared to Rockrose pollen (Tukey HSD, p>0.05). Overall, we discovered that the higher-quality Castanea diet had the ability to numerically reduce mortality in the presence of IAPV infection compared to the lower-quality Rockrose diet (Figure \ref{fig:mortality} A).

@@

Pathway analysis of the Castanea DEGs revealed enriched (Benjamini correction < 0.05) Wnt signaling, hippo signaling, and dorso-ventral axis formation pathways, as well as pathways related to circadian rhythm, mRNA surveillance, insulin resistance, inositol phosphate metabolism, FoxO signaling, ECM-receptor interaction, phototransduction, Notch signaling, JaK-STAT signaling, MAPK signaling, and carbon metabolism (Table \ref{tbl:CastaneaPathways}). Pathway analysis of the Rockrose DEGs revealed pathways related to terpenoid backbone biosynthesis, homologous recombination, SNARE interactions in vesicular transport, aminoacyl-tRNA biosynthesis, Fanconi anemia, and pyrimidine metabolism (Table \ref{tbl:RockrosePathways}).

@@@ Not enough DEGs to form pathways for virus @@@

@@

>>>>

Mortality rates of honeybees 72 hour post-inoculation significantly differed among the treatment groups (mixed model ANOVA across all treatment groups, df=3, 55; F=10.07; p<2.18e-05). The effect of virus treatment (mixed model ANOVA, df=1, 55; F=24.343; p<7.84e-06) and diet treatment (mixed model ANOVA, df=1, 55; F=5.796; p<0.0194) were significant, but the interaction between the two factors (mixed model ANOVA, df=1, 55; F=0.062, p=0.8039) was not significant. The virus treatment was significant: For a given diet, honeybees exposed to the virus showed significantly higher mortality rate than honeybees not exposed to the virus (Tukey HSD, p<0.05). Without virus exposure, there was only a numerical reduction in mortality rate for bees fed Castanea pollen compared to Rockrose pollen (Tukey HSD, p>0.05). Similarly, with virus exposure, there was only a numerical reduction in mortality rate for bees fed Castanea pollen compared to Rockrose pollen (Tukey HSD, p>0.05). Overall, we discovered that the higher-quality Castanea diet had the ability to numerically reduce mortality in the presence of IAPV infection compared to the lower-quality Rockrose diet (Figure \ref{fig:mortality} A).

@@

Pathway analysis of the Castanea DEGs revealed enriched (Benjamini correction < 0.05) Wnt signaling, hippo signaling, and dorso-ventral axis formation, as well as pathways related to circadian rhythm, mRNA surveillance, insulin resistance, inositol phosphate metabolism, FoxO signaling, ECM-receptor interaction, phototransduction, Notch signaling, JaK-STAT signaling, MAPK signaling, and carbon metabolism (Table \ref{tbl:CastaneaPathways}). Pathway analysis of the Rockrose DEGs revealed pathways related to terpenoid backbone biosynthesis, homologous recombination, SNARE interactions in vesicular transport, aminoacyl-tRNA biosynthesis, Fanconi anemia, and pyrimidine metabolism (Table \ref{tbl:RockrosePathways}).

It was difficult to perform a pathway analysis with so few DEGs (n = 43) in our virus main effect study. As a result, we focused on individual genes and their known functionalities (Table \ref{tbl:virusGenes}). Of the 43 virus-related DEGs, only 10 of them successfully mapped with DAVID software. These genes had implications in the recognition of pathogen-related lipid products and the cleaving of transcripts from viruses, as well as involvement in ubiquitin and proteosome pathways, transcription pathways, apoptopic pathways, oxidoreductase processes, and several more functions (Table \ref{tlb:virusGenes}).

@@

\begin{table}[H]
  \includegraphics[width=\textwidth]{Images/virusGenes}
  \caption{Known functions of the mapped subset of 43 DEGs in the virus main effect of our study. Whether the gene was overrepresented in the virus or non-virus group is also indicated for both our study and the Galbraith study. Functionalities were extracted from Flybase, National Center for Biotechnology Information, and The European Bioinformatics Institute databases.}
  \label{tbl:virusGenes}
\end{table}
